Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-08 popl24/hyperprop.tex
Update hyperprop.tex

In this section, we formulate a new hyperproperty that we show is
sound for passive security in the real/ideal model, called
\emph{noninterference modulo output ($\NIMO$)}. We do not claim
completeness with respect to passive security, but soundness
guarantees that enforcement of $\NIMO$ in our analyses implies passive
security. In Section \ref{section-bruteforce} we show how $\NIMO$ can
be automatically enforced in a brute-force manner, and in Section
\ref{section-composition} we show how $\NIMO$ can be refined to obtain
compositional properties supporting efficient, scalable enforcement of
complex protocols that incorporate modular subprotocols, using
both YGC and GMW circuits as examples where gates are
subprotocols. The latter methodology demonstrates a particular
advantage of our intensional formulation.

\subsection{Passive Security and the Real/Ideal Model}
\label{section-hyperprop-passive}
Here we briefly summarize the formal definition of MPC security. For a
more detailed discussion the reader is referred to \cite{evans2018pragmatic}.
In this paper, we will consider the \emph{passive} aka
semi-honest aka honest-but-curious variant. In this threat
model, protocol participants can be corrupted, but all clients
follow the rules of the protocol- as opposed to the
\emph{active} aka malicious variant where participants
are allowed to break these rules. In the passive model, the
vulnerability is through information leaked to the adversary
through the views of corrupted participants. While the passive
model also assumes that any clients can potentially be
corrupted, it assumes that no more than half will be-
i.e., it assumes an \emph{honest majority}.

@@

The simulator is represented by a probabilistic algorithm $\SIM_C$,
aka a \emph{simulation}, that is parameterized by a corrupt inputs and
the output of an ideal functionality, and that returns a set of
adversarial views (as a memory) with some probability. Given
corrupt inputs $\store$ and ideal functionality output $v$,  
we write:
$$
\prob(\SIM_C(\store,v) = \store')
$$
to denote the probability that $\SIM_C(\store,v)$
returns corrupt views $\store'$ as a result. We can then define the
probability distribution of corrupt views reconstructed
by the simulator as follows:
\begin{definition}
  Given $C$, $\store$, and $v$, we write $\progd(\SIM_C(\store,v))$ to
  denote the distribution of corrupt views reconstructed by the
  simulation, where for
  all $\store' \in \mems(V)$:
  $$
  \progd(\SIM_C(\store,v))(\store')\ \defeq\ \prob(\SIM_C(\store,v) = \store') 
  $$
\end{definition}

@@

  Now, since the random tape is selected in simulation from the same distribution
  that we assume for the real world, after selection of $\store'$ the
  probability that any particular $\store^{\SIM}_{V_C}$ is returned is by definition:
  $$
  \progd(\prog)(\store^{\SIM}_{V_C} | \store')
  $$
  Furthermore, since we assume that $\prog$ correctly implements $\idealf$, this
  means:
  $$
  \store_S =_C \store' \wedge
     \condd{\progd(\prog)}{\{ \outv \}}{\store_S} =
     \condd{\progd(\prog)}{\{ \outv \}}{\store'}
  $$
  so by the definition of noninterference modulo output
  any choice of $\store'$ yields the same distribution $\condd{\progd(\prog)}{V_C}{\store_S}$.
  Therefore by definition
  $
   \progd(\SIM_C(\store_{S_C},\idealf(\store))) = \condd{\progd(\prog)}{V_C}{\store_S}
  $.
\end{proof}

>>>>

In this section, we formulate a new hyperproperty that we show is
sound for passive security in the real/ideal model, called
\emph{noninterference modulo output ($\NIMO$)}. We do not claim
completeness with respect to passive security, but soundness
guarantees that enforcement of $\NIMO$ in our analyses implies passive
security. In Section \ref{section-bruteforce} we show how $\NIMO$ can
be automatically enforced in a brute-force manner and in Section
\ref{section-composition} we show how $\NIMO$ can be refined to obtain
compositional properties supporting efficient, scalable enforcement of
complex protocols that incorporate modular subprotocols, using
both YGC and GMW circuits as examples where gates are
subprotocols. The latter methodology demonstrates a particular
advantage of our intensional formulation.

\subsection{Passive Security and the Real/Ideal Model}
\label{section-hyperprop-passive}
Here we briefly summarize the formal definition of MPC security. For a
more detailed discussion, the reader is referred to \cite{evans2018pragmatic}.
In this paper, we will consider the \emph{passive} aka
semi-honest aka honest-but-curious variant. In this threat
model, protocol participants can be corrupted, but all clients
follow the rules of the protocol- as opposed to the
\emph{active} aka malicious variant where participants
are allowed to break these rules. In the passive model, the
vulnerability is through information leaked to the adversary
through the views of corrupted participants. While the passive
model also assumes that any clients can potentially be
corrupted, it assumes that no more than half will be-
i.e., it assumes an \emph{honest majority}.

@@

The simulator is represented by a probabilistic algorithm $\SIM_C$,
aka a \emph{simulation}, that is parameterized by corrupt inputs and
the output of an ideal functionality, and that returns a set of
adversarial views (as a memory) with some probability. Given
corrupt inputs $\store$ and ideal functionality output $v$,  
we write:
$$
\prob(\SIM_C(\store,v) = \store')
$$
to denote the probability that $\SIM_C(\store,v)$
returns corrupt views $\store'$ as a result. We can then define the
probability distribution of corrupt views reconstructed
by the simulator as follows:
\begin{definition}
  Given $C$, $\store$, and $v$, we write $\progd(\SIM_C(\store,v))$ to
  denote the distribution of corrupt views reconstructed by the
  simulation, where for
  all $\store' \in \mems(V)$:
  $$
  \progd(\SIM_C(\store,v))(\store')\ \defeq\ \prob(\SIM_C(\store,v) = \store') 
  $$
\end{definition}

@@

  Now, since the random tape is selected in simulation from the same distribution
  that we assume for the real world, after selection of $\store'$ the
  probability that any particular $\store^{\SIM}_{V_C}$ is returned is by definition:
  $$
  \progd(\prog)(\store^{\SIM}_{V_C} | \store')
  $$
  Furthermore, since we assume that $\prog$ correctly implements $\idealf$, this
  means:
  $$
  \store_S =_C \store' \wedge
     \condd{\progd(\prog)}{\{ \outv \}}{\store_S} =
     \condd{\progd(\prog)}{\{ \outv \}}{\store'}
  $$
  so by the definition of noninterference modulo output,
  any choice of $\store'$ yields the same distribution $\condd{\progd(\prog)}{V_C}{\store_S}$.
  Therefore by definition
  $
   \progd(\SIM_C(\store_{S_C},\idealf(\store))) = \condd{\progd(\prog)}{V_C}{\store_S}
  $.
\end{proof}
